Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-11-22 edubots_surveys.Rnw
Highlight changes

Our intention from the beginning was to try to gather a sufficient amount of
responses in all sectors, as well as cover different sectors of higher
education. In doing so, an online survey was administered (i.e., Google Form),
in Spanish, which was intended to be answered in a very short amount of
time. Initially, our intention was to mirror the questions used in
\cite{MoraChatbots2021:anon}; however, an initial exploration of results led us
to create a second survey. The \textcolor{blue}{new survey} items focused on the use of messaging apps
in the teaching practice, the type of chatbot use cases that teachers consider
useful to be used in their teaching, and the type of interactions that teachers
prefer to have with their students while using messaging apps in their teaching.

The {\bf initial survey} was done in two separate Google forms, one for
university and other for tertiary non-university teachers. Questions and
responses were the same, except for the type of tertiary degrees that
\textcolor{blue}{were considered}. In both cases, we used mainly mailing lists, as well as Telegram groups,
to spread the link to the form. The university form was spread in Spanish
(mainly Andaluc\'{\i}a and Galicia) universities, and also Costa Rica and
Mexico. The tertiary non-university teachers are based mainly in
Andaluc\'{\i}a. Dissemination and answers took place in the first quarter of
2021, post-pandemic and while, at least in Spain, many universities had
mandatory virtual teaching.

>>>>

\textcolor{blue}{This study aims to collect rich data about the use of messaging applications and chatbots
by educators in both universities and colleges\footnote{In Spain, they are called simply high schools, and deliver
tertiary or associated degrees that do not have the consideration of university degrees}.
To achieve this goal, an online survey was designed and developed using Google Forms
in Spanish}. Initially, the intention was to mirror the questions used in
\cite{MoraChatbots2021:anon}; which explored students' views about the use of messaging applications in classrooms.
However, the initial exploration of results led us
to create a second survey in order to collect more data about educators' preferences in particular. The \textcolor{blue}{new survey} items 
focused on the use of messaging apps in the teaching practice, the type of chatbot use cases that teachers consider
useful to be used in their teaching, and the type of interactions that teachers
prefer to have with their students while using messaging apps in their teaching.

The {\bf initial survey} was done in two separate Google forms, one for
university and other for tertiary non-university teachers. Questions and
responses were the same, except for the type of tertiary degrees that
\textcolor{blue}{were considered. The survey was piloted by the authors of the paper and their colleagues before using it in the 
study.  All the comments collected from this trial were incorporated in the survey.
We used mainly mailing lists, as well as Telegram groups,
to post the survey link to reach out to more educators}. The university form was sent to Spanish
(mainly Andaluc\'{\i}a and Galicia) universities, and also  universities in Costa Rica and
Mexico. The tertiary (non-university/college) teachers were based mainly in
Andaluc\'{\i}a. Dissemination and answers took place in the first quarter of
2021, post-pandemic and while, at least in Spain, many universities had
mandatory virtual teaching.
